% Created 2021-04-01 Thu 21:35
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Mayer Goldberg}
\date{\today}
\title{Mayer Goldberg's Homepage}
\hypersetup{
 pdfauthor={Mayer Goldberg},
 pdftitle={Mayer Goldberg's Homepage},
 pdfkeywords={Mayer Goldberg, Department of Computer Science, Ben-Gurion University, lambda calculus, combinatory logic, pi-calculus, functional programming, coq, proof assistant, nuprl, object-oriented programming, Scheme, ML, Erlang, Lua, Smalltalk, continuations, interpreters, compilers, decompilation, compilation, code obfuscation, programming languages, semantics, threaded code, forth, latin, israel, israeli police, lying cops, israeli police lying},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\begin{quote}
Everybody seems to understand that astronomers do astronomy because
astronomy is interesting. Why don't they understand that I do computer
science because computer science is interesting? And that I'd do it
regardless of whether or not it made money for anybody? 

--- \emph{Donald E. Knuth}
\end{quote}

\section{Contact Information}
\label{sec:org437284f}

\begin{itemize}
\item Email: \href{mailto:gmayer@little-lisper.org}{gmayer@little-lisper.org}. All email, from all other accounts,
gets forwarded to this account.
\item Office: Building 37 (Alon, אלון) room 106, mailbox 44
\item Office hours (for the Spring Semester 2021)
\begin{itemize}
\item For my functional programming course: Mondays, 14-16
\item For the Teaching Committee: Mondays, 19-21
\end{itemize}
\item Telephones: Voice (+972)(0)8-647-7873, FAX (+972)(0)8-647-7650
\item Professional mailing address: \href{mailto:gmayer@little-lisper.org}{Mayer Goldberg}, \href{http://www.cs.bgu.ac.il/}{Department of Computer
Science}, \href{http://www.bgu.ac.il/}{Ben Gurion University}, PO Box 653, Beer Sheva 84105,
Israel.
\item Personal mailing address: Mayer \& Sharon Goldberg, PO Box 15161,
Beer Sheva, 84121, Israel
\end{itemize}

\section{Research}
\label{sec:orga32323c}
\begin{enumerate}
\item Research Interests
\label{sec:org44b2f54}
\begin{itemize}
\item The Lambda Calculus
\item Programming Languages
\item Functional Programming
\item Object-Oriented Programming
\item Computational Reflection
\item Continuations \& Control
\item Interpretation \& Compilation
\item Automated theorem proving (\href{./coq.html}{Coq}, \href{http://www.nuprl.org/}{NuPRL}, etc)
\end{itemize}
\item Research Students
\label{sec:orgcad0b0a}
\begin{enumerate}
\item Present research students
\label{sec:org7332294}
\item Past research students
\label{sec:orgaa6d14d}
\begin{itemize}
\item Lior Zur-Lotan (MSc, 2021)
\item Valery Frolov (MSc, 2012)
\item Guy Wiener (PhD, 2012)
\item Sonia Margulis (MSc, 2011)
\item Avi Shefi (MSc, 2009)
\item Yelena Lev (MSc, 2008)
\item Yigal Greenshpun (MSc, 2007)
\item Guy Wiener (MSc, 2007)
\item Assaf Shemesh (MSc, 2006)
\end{itemize}
\end{enumerate}
\end{enumerate}

\section{Teaching}
\label{sec:org70825ef}
\begin{itemize}
\item Introduction to Functional Programming, Spring 2021
\item Introduction to Compiler Construction, Fall 2020
\item \href{./tutorials.html}{My tutorials}
\item \href{./special.html}{My policies on extensions, exemptions \& special requests}
\item \href{./projects.html}{Undergraduate projects I am offering (פרוייקטים לתואר ראשון)}
\end{itemize}

\section{Departmental duties}
\label{sec:orgf2ce4c4}
\begin{itemize}
\item \href{./tc.html}{Freshman teaching committee}
\end{itemize}
\section{Personal Interests}
\label{sec:org98260d9}
\begin{itemize}
\item \href{./proglang/proglang.html}{Learning interesting programming languages}
\item \href{./personal/books.html}{Books}
\item \href{./personal/latin.html}{Latin}
\end{itemize}

\section{\emph{A website that is seriously out-of-date\ldots{}}}
\label{sec:org604b545}

My apologies!

Since around 2014, I was having difficulties updating and managing my website. A combination of technical difficulties, changing platforms, and lack of time, all prevented me from keeping my website up-to-date. Anyway, I think I managed to solve many of the old problems, and get my website up and running again. I'm updating it continuously. So please stay turned! \(\ddot\smile\)
\end{document}
