% Created 2021-04-01 Thu 22:47
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Mayer Goldberg}
\date{\today}
\title{Teaching Committee}
\hypersetup{
 pdfauthor={Mayer Goldberg},
 pdftitle={Teaching Committee},
 pdfkeywords={Mayer Goldberg, Teaching Committee, Department of Computer Science, Ben-Gurion University, israel},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{Synopsis}
\label{sec:org3ec8e9c}

I serve as the freshmen advisor and undergraduate chairman (יועץ שנה א', ויו"ר ועדת הוראה לשנה א') at the \href{http://www.cs.bgu.ac.il/}{department of computer science} at \href{http://www.bgu.ac.il/}{Ben-Gurion University}. 

\section{How to contact me}
\label{sec:org23d015c}

\begin{center}
\begin{tabular}{ll}
Name & Mayer Goldberg\\
Email & \href{mailto:gmayer@little-lisper.org}{gmayer@little-lisper.org}\\
Office & Building 37 (Alon, אלון), room 106, mailbox 44\\
Office hours (semester א) & Mondays, 19:00--21:00\\
Telephones & Voice 08-647-7873, FAX 08-647-7650\\
\end{tabular}
\end{center}

\section{General guidelines}
\label{sec:org4f86cbd}

Please understand that:
\begin{itemize}
\item No decisions are made \textquotedblleft{}on the spot,\textquotedblright{} regardless of what you tell me
\item All decisions are taken offline, after deliberation with other members of the department and the relevant faculty (either Natural Sciences of Engineering, depending on what program you are in), with all relevant documentation at hand, and in particular, with your academic transcript before us
\item You are welcome to come to my office hours, but please keep in mind that on all personal academic matters, I will probably direct you to the the webpage for contacting the student secretariat (מַזְכִּירוּת הַסְּטוּדֶנְטִים)
\item You are welcome to show up to my office hours, or to \href{mailto:gmayer@little-lisper.org}{send me email}, but the best way to contact me is via the \href{https://cs-sr.cs.bgu.ac.il/}{online, departmental form (מַעֲרֶכֶת פְּנִיּוֹת הַסְּטוּדֶנְטִים)}
\end{itemize}

\section{Issues that come up frequently}
\label{sec:orgb103d49}

\begin{itemize}
\item If you \textbf{seek authorization for a course}, or \textbf{מועד מיוחדin a course you took}, please go to the undergraduate secretariat on the first floor [of building \#37], and fill and submit the appropriate form. You should support \& substantiate any claims you make with appropriate documentation, and include those with your form. There is no need to speak with me in advance.
\item If you are continuing your studies at our department, you have already been admitted, and \textbf{would like to get an exemption (פטור) from various courses in your program}, on the strength of courses you took elsewhere, as part of another program, then you need to do the following:
\begin{itemize}
\item Download the a request להכרה בקורסיםfrom the website of the Faculty of Natural Sciences.
\item Fill in the form, listing the courses you took on the strength of which you are asking for the exemption, the syllabus for each such course, and the courses from which you are asking for an exemption.
\item Submit the form, including the syllabi, to the undergraduate secretariat.
\end{itemize}
\item For inquiries about the \textbf{קורס רענון במתמטיקה} in the מכינה, please consult the \href{http://in.bgu.ac.il/acadsec/preacad/Pages/accepted.aspx}{מכינה's website} in order to see the syllabus, list of topics, bibliography, timetable, etc.
\item If you are unhappy about the grade you received in a course, you need to take this matter with your instructor. Unless these are in blatant, obvious violation of the regulations of the university \& faculty, I do not interfere with the grading policies in your courses.
\item If you are falling behind in your courses, please contact \href{http://in.bgu.ac.il/Dekanat/Pages/default.aspx}{דיקנאט הסטודנטים}, and join התוכנית למניעת נשירה. From what we hear, their program is effective in helping students get back on track.
\item If you suffer from disabilities that hamper your academic work (be they learning disabilities, physical, psychological, etc), please contact המדור לקידום סטודנטיםat the \href{http://in.bgu.ac.il/Dekanat/Pages/default.aspx}{דיקנאט הסטודנטים}. They have a wide range of programs to help you make the most of your academic experience at BGU. Keep in mind that assessment of medical or learning disabilities takes time to complete, and many of the benefits to which you may be entitled will be predicated on the results of this assessment. If you know you are going to require their help, please start the process as soon as possible.
\item Information concerning מועדי ג':
\begin{itemize}
\item מועדג'is granted for the conditions specified in תקנון הבחינות. Exceptions to תקנון הבחינות \emph{will only be entertained} in situations that \emph{greatly resemble} the conditions specified in תקנון הבחינות.
\item If you've taken \emph{both} מועדא'and מועד ב'in a course, then \emph{under no circumstances} will you receive מועד ג'.
\item The authority to grant מועדי ג'lies solely with the teaching committee, and not with the instructor of the course. We on מועדי ג' on the merits of the case, and not on the request of the instructor. In other words, *even if your instructor promised you מועד ג', this means nothing until the teaching committee decides you should have מועד ג'*.
\end{itemize}
\end{itemize}

For all other matters, \href{mailto:gmayer@little-lisper.org}{write me an email} or come and see me in person during my office hours. 
\end{document}
